Model details and results

### 2023-09-15 notebook/model-details.qmd
Add ordered beta illustration + model results table

---
title: Model details
---

@@

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(brms)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(patchwork)
library(scales)
library(glue)
library(gt)
library(gtExtras)

@@

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta, m_full_interaction_ordbeta))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))
```

```{r calculate-model-times}
models <- tribble(
  ~model_name, ~model,
  "Full model", m_full_ordbeta,
  "Full model with `local_connect * years_since_law` interaction", m_full_interaction_ordbeta,
) |> 
  mutate(duration = map(model, ~{
    .$fit |> 
      rstan::get_elapsed_time() |> 
      as_tibble() |> 
      summarize(total = as.duration(max(warmup + sample)))
  })) |> 
  select(-model) |> 
  unnest(duration)

@@

>>>>

---
title: Model details and results
---

@@

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(scales)
library(glue)
library(gt)
library(gtExtras)
library(modelsummary)

@@

# Load targets
tar_load(ongo)
tar_load(c(m_full_ordbeta))
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))

theme_set(theme_ongo())
```

# Model run times

```{r calculate-model-times}
models <- tribble(
  ~model_name, ~model,
  "Full model", m_full_ordbeta,
) |> 
  mutate(duration = map(model, ~{
    .$fit |> 
      rstan::get_elapsed_time() |> 
      as_tibble() |> 
      summarize(total = as.duration(max(warmup + sample)))
  })) |> 
  select(-model) |> 
  unnest(duration)

@@

# Model results

Raw coefficients aren't super useful for interpreting things, but here's a table of them for fun.

```{r results-table}
modelsummary(
  m_full_ordbeta,
  statistic = "[{conf.low}, {conf.high}]",
  ci_method = "hdi",
  metrics = c("R2"),
  output = "gt"
) |> 
  opts_theme()
```
